A BenchMark Test Research

### 2024-08-12 draft.tex
update design section

\section{Design and Implementation}
\label{tec}
Follow several steps and get the result.
\subsection{Linux Environment}
in Windows system or MacOS system, install a virtual machine like VMware and install Ubuntu image file.
install PaSh through this command
\begin{minted}[fontsize=\footnotesize]{shell}
./cleanup.sh
\end{minted}

@@

\section{Conclusion}
\label{conclusion}

\sys's implementation are all open source and available for download:
\href{https://github.com/something/else}{github.com/something/else}.

>>>>

\section{Design and Implementation}
\label{tec}
To achieve the desired outcome, adhere to the following sequential steps:
\subsection{Linux Environment and PaSh}
\textbf{Virtual Machine Installation:} On your Windows or macOS system, begin by installing a virtual machine software such as VMware. Proceed to set up an Ubuntu image file within this virtual environment.\newline
\textbf{Installing PaSh:} Install the PaSh by executing the following command in terminal:
\begin{minted}[fontsize=\footnotesize]{shell}
wget https://raw.githubusercontent.com/binpash/pash/main/scripts/up.sh
sh up.sh
export PASH_TOP="$PWD/pash/"
## Run PaSh with echo hi
"$PASH_TOP/pa.sh" -c "echo hi"
\end{minted}
\subsection{Benchmark}
Install the binpash/benchmark repository by executing the following command in terminal:
\begin{minted}[fontsize=\footnotesize]{shell}
git clone https://github.com/binpash/benchmarks.git
\end{minted}
For the vast majority of projects, run by imitating the Example section.
If there are special requirements, refer to the README file.

@@

\section{Discussion}
\label{dis}

The file-enc has some bug.
The first one is that in run.sh input\_dir is wrong and it needs go to the folder inputs.
Change like this can solve this bug.
\begin{minted}[fontsize=\footnotesize]{shell}
# in run.sh wrong in line 9 and 12
    input_dir="inputs/pcap_data_small" # should go to inputs
\end{minted}

The second is that in compress\_files.sh and in encrypt\_files.sh and miss a folder too.
\begin{minted}[fontsize=\footnotesize]{shell}
# in compress_files.sh, wrong in line 8
cat $1/$item | gzip -1 -c > $2/$output_name #miss $1
\end{minted}

\begin{minted}[fontsize=\footnotesize]{shell}
# in encrypt_files.sh, wrong in line 17
cat $1/$item | pure_func > $2/$output_name # miss $1 too
\end{minted}
After add the folder, scripts can run successfully.

\section{Conclusion}
\label{conclusion}
The paper test several repositories in benchmark and evaluate the correctness and efficiency. Most of the shell scripts may output in a wrong format which cause the low correct rate, while perfrom well in the large-scale data. \newline
All the data are open source and available for download: \href{https://github.com/yiz853793/benchmark-test}{https://github.com/yiz853793/benchmark-test.}
